Hydra Battles and Cie

### 2021-07-07 doc/hydras.tex
apply suggested changes

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean,  Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

>>>>

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean, Jéremy Damour,   Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this library and  document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

### 2021-07-07 doc/part-hydras.tex
apply suggested changes

%The following definitions allow us to make implicit several guessable arguments.
\label{sect:on-lt-notation}
\label{sect:on-le-notation}
\begin{Coqsrc}
Definition on_t  {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : ON lt compare} := A.

Definition ON_compare {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : ON lt compare} := compare.

Definition ON_lt {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} := lt.

Infix "o<" := ON_lt : ON_scope.

Definition ON_le  {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} :=
  clos_refl _ ON_lt.

Infix "o<=" := ON_le : ON_scope.
\end{Coqsrc}

@@

\subsection{Ordinal notations and  termination measures}
\label{sect:measure-ON}

The following lemma (together with the type class mechnism) allows us to define termination measures over any ordinal notation. It is just an application of  the libraries \texttt{Coq.Wellfounded.Inverse\_Image}
and  \texttt{Coq.Wellfounded.Inclusion}.

\begin{Coqsrc}
Definition measure_lt {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : ON lt compare}
            {B : Type} (m : B -> A) : relation B :=
             fun x y => on_lt (m x) (m y).

Lemma wf_measure  {A:Type}(lt: relation A)
            {compare : A -> A -> comparison}
            {on : ON lt compare}
            {B : Type}
            (m : B -> A):  well_founded (measure_lt m). 
\end{Coqsrc}

A simple example of application is given in Sect.~\vref{sect:merge-example}.

>>>>

We give  also a few handy definitions and lemmas for any ordinal notation.

\label{sect:on-lt-notation}
\label{sect:on-le-notation}
\begin{Coqsrc}
Section Definitions.

  Context  {A:Type}{lt : relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare}.

  #[using="All"]
   Definition ON_t := A.

  #[using="All"]
   Definition ON_compare := compare.

  #[using="All"]
   Definition ON_lt := lt.

  #[using="All"]
   Definition ON_le:  relation A := leq lt.

  #[using="All"]
   Definition measure_lt {B : Type} (m : B -> A) : relation B :=
    fun x y =>  ON_lt (m x) (m y).

  #[using="All"]
   Lemma wf_measure {B : Type} (m : B -> A) :
    well_founded (measure_lt m).

  #[using="All"]
   Definition ZeroLimitSucc_dec :=
    forall alpha,
      {Least alpha} +
      {Limit alpha} +
      {beta: A | Successor alpha beta}.

  (** The segment called [O alpha] in Schutte's book *)

  #[using="All"]
   Definition bigO 
   (a: A) : Ensemble A := fun x: A => lt x a.

End Definitions.

Infix "o<" := ON_lt : ON_scope.
Infix "o<=" := ON_le : ON_scope.
\end{Coqsrc}

@@

% \subsection{Ordinal notations and  termination measures}
% \label{sect:measure-ON}

% The following lemma (together with the type class mechnism) allows us to define termination measures over any ordinal notation. It is just an application of  the libraries \texttt{Coq.Wellfounded.Inverse\_Image}
% and  \texttt{Coq.Wellfounded.Inclusion}.

% \begin{Coqsrc}
% Definition measure_lt {A:Type}{lt: relation A}
%             {compare : A -> A -> comparison}
%             {on : ON lt compare}
%             {B : Type} (m : B -> A) : relation B :=
%              fun x y => on_lt (m x) (m y).

% Lemma wf_measure  {A:Type}(lt: relation A)
%             {compare : A -> A -> comparison}
%             {on : ON lt compare}
%             {B : Type}
%             (m : B -> A):  well_founded (measure_lt m). 
% \end{Coqsrc}

% A simple example of application is given in Sect.~\vref{sect:merge-example}.
